### 2014-06-17 1_introduction/introduction.tex
auto

%How do others solve this problem?
%Briefly What are their solution? what problems they cannot yet solve?
While
                the statistical model for SAR is quite well understood,
the
                understanding of the POLSAR statistical model trails behind.
The
                complex POLSAR data have been statistically modelled as
                following the complex Wishart distribution, which
                apparently is multi-dimensional, complex and
                un-intuitive.
There
                have been a few published scalar statistical models for
                POLSAR, but none of them fit the dual criteria of being
                highly representative of the data and at the same time
                lead to scalar discrimination measures.
There
                are also a few POLSAR discrimination measures proposed,
                but all of them are based on the likelihood test
                statistics, which so far have only shown to be based on an
                asymptotic distribution.

@@

As both the SAR and POLSAR data are stochastic in nature, many of the associated data processing techniques, such as speckle filtering has been put into the framework of statistical estimation.
For such application, the research methodology is based extensively on the statistical estimation framework. 
The framework consists of three stages:

>>>>

%How do others solve this problem?
%Briefly What are their solution? what problems they cannot yet solve?
While
                the statistical model for SAR is quite well understood,
the
                understanding of the POLSAR statistical model trails behind.
The
                complex POLSAR data have been statistically modelled as
                following the complex Wishart distribution, which
                apparently is multi-dimensional, complex and
                un-intuitive.
There
                have been a few published scalar statistical models for
                POLSAR, \cite{Alberga_2008_IJRS_4129, Joughin_1994_TGRS_562, Lee_1994_TGRS_1017, Touzi_1996_TGRS_519, Barakat_1985_IJOptics, Eliyahu_1993_PhysRevE_2881, Brosseau_1995_AppliedOptics_4788} but none of them fit the dual criteria of being
                highly representative of the data and at the same time
                lead to scalar discrimination measures.
There
                are also a few POLSAR discrimination measures proposed \cite{Lee_1994_IJRS_2299, Kersten_2005_TGRS_519, Lee_2011_IGARSS_3740, Cao_2007_TGRS_3454, Conradsen_2003_TGRS_4},
                but all of them are based on the likelihood test
                statistics, which so far have only shown to be based on an
                asymptotic distribution.

@@

As both the SAR and POLSAR data are stochastic in nature, many of the associated data processing techniques, such as speckle filtering have been put into the framework of statistical estimation.
For such application, the research methodology is based extensively on the statistical estimation framework. 
The framework consists of three stages:
